---
title: "PosterDataProcessing"
author: "Devin Gee and Lydia Zhang"
date: "2023-04-18"
output:
  html_document: default
  pdf_document: default
---


##                            Does Educational Path Relate to Health?


```{r cars, echo =FALSE}

knitr::opts_chunk$set(cache=TRUE,
                      message=FALSE, warning=FALSE,
                      fig.path='figs/',
                      cache.path = '_cache/',
                      fig.process = function(x) {
                      x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
                      if (file.rename(x, x2)) x2 else x
                      }, tidy.opts=list(width.cutoff=60),tidy=TRUE)

#font_import()
#loadfonts(device = "win")
setwd("C:/Users/devin/OneDrive/Documents/QTM302/Data Descriptor")
```

### Import Packages

```{r}
library(formatR)
library(kableExtra)
library(tidyverse)
library(ggplot2)
library(reshape2)
library(RColorBrewer)
library(extrafont)
```


### Read in Files
```{r pressure, echo=FALSE, warnings = FALSE}
#Wave IV Data
df_1<-readr::read_tsv("C:/Users/devin/OneDrive/Documents/QTM302/Data Descriptor/data/dataOfInt/DS22-Wave-IV-In-Home-Questionnaire.tsv")

#Select 2008 education level data
education <- select(df_1,AID,H4ED2)
colnames(education) <- c("ID","Education_level_2008")

#Wave V Data
df_2<-readr::read_tsv("C:/Users/devin/OneDrive/Documents/QTM302/Data Descriptor/data/fullData/DS0032/21600-0032-Data.tsv")

#Select 2018 education level data
education2 <- select(df_2,AID,H5OD11)
colnames(education2) <- c("ID","Education_level_2018")

```


```{r, warnings = FALSE}

#Collect Wave 5 biomarker data
WaveV <- lapply(paste0("C:/Users/devin/OneDrive/Documents/QTM302/Data Descriptor/data/fullData/DS00",32:42
                       ,"/21600-00",32:42,"-Data.tsv"), read_tsv)
 
biomarkerVDataset <- c(WaveV[3:10])
```

```{r, warnings = FALSE}
#Import
df_2<-readr::read_tsv("C:/Users/devin/OneDrive/Documents/QTM302/Data Descriptor/data/dataOfInt/Lydia/medication.tsv")
medication <- select(df_2,AID,H5MEDSRC, H5ECRP8)
colnames(medication) <- c("ID","BloodPressure","Inflammatory")
medication_comb<-
  medication %>% transmute(ID = ID, BloodPressure+ Inflammatory)
head(medication_comb)
```


```{r, warnings = FALSE}
df_3 <-readr::read_tsv("C:/Users/devin/OneDrive/Documents/QTM302/Data Descriptor/data/dataOfInt/Lydia/psy.tsv")
Psy <- select(df_3, AID, H2HS5)
colnames(Psy) <- c("ID","Psyc_Consult")
```

### Join Biomarker Data frames
```{r, warnings = FALSE}
biomarkerVJoined <- left_join(data.frame(biomarkerVDataset[2]),
                              data.frame(biomarkerVDataset[8]), by= c("AID","H5Q045D")) 

biomarkerVJoined <- left_join(data.frame(biomarkerVJoined),
                              data.frame(biomarkerVDataset[6]), by= c("AID","H5Q045F")) 

biomarkerVJoined <- left_join(data.frame(biomarkerVJoined),
                              data.frame(biomarkerVDataset[4]), by= c("AID","H5FASTTM","H5Q045B")) 

biomarkerVJoined <- left_join(data.frame(biomarkerVJoined),
                              data.frame(biomarkerVDataset[1]), by= c("AID","H5ARMINS","H5ARMCIR","H5ARM")) 

biomarkerVJoined <- left_join(data.frame(biomarkerVJoined),
                              data.frame(biomarkerVDataset[3]), by= c("AID")) 

biomarkerVJoined <- left_join(data.frame(biomarkerVJoined),
                              data.frame(biomarkerVDataset[5]), by= c("AID"))

biomarkerVJoined <- left_join(data.frame(biomarkerVJoined),
                              data.frame(biomarkerVDataset[7]), by= c("AID")) 
```









```{r, warnings = FALSE}
full_list <- list(education,education2,medication_comb,Psy)
table <- 
  full_list %>% reduce(full_join, by='ID')

colnames(table)[4] <- "Medication_Use"
table <- mutate(table, Medication_Use = ifelse(is.na(Medication_Use), "No Reported Use","Reported Use"))

#sum(is.na(table$Psyc_Consult))
table <- na.omit(table)
```

```{r, warnings = FALSE}
# if you graduated during the survey years you would be misclassified
recodedTable <- mutate(table, Education_level_2008= ifelse(table$Education_level_2008 < 7, 0,1 ), Education_level_2018= ifelse(table$Education_level_2018 < 10, 0,1 ))
#0 if it stayed the same 1 if it changed
recodedTable <- mutate(recodedTable, Education_Change = case_when(table$Education_level_2008 < 7 & table$Education_level_2018 >= 10 ~ 1, TRUE ~ 0))
#0 if they are non graduate, 1 if they are traditional graduate, 2 if they are non traditional graduate
recodedTable <- mutate(recodedTable, Classification = case_when(recodedTable$Education_level_2008 == 0 & recodedTable$Education_Change == 0 ~ "Non-College Graduates", recodedTable$Education_level_2008 == 1 & recodedTable$Education_Change == 0 ~ "Traditional College Graduates", recodedTable$Education_Change == 1 ~ "Non-Traditional College Graduates"), Psyc_Consult= ifelse(table$Psyc_Consult == 0, "No Reported Use","Reported Use" ))
```


```{r, warnings = FALSE}
contigencytable <-table(recodedTable$Classification, recodedTable$Medication_Use)
mytest <- chisq.test(contigencytable)
mytest
```






``````{r, warnings = FALSE}
par(mar = c(1, 1, 1, 1))
contigencytable <-table(recodedTable$Classification, recodedTable$Psyc_Consult)
chiTest <- chisq.test(contigencytable)
chiDf <- melt(prop.table(contigencytable, margin = 1))

ggplot(data=chiDf, aes(x=Var1, y=Var2, fill=value)) +
  geom_tile() +
  scale_fill_gradientn(colours=c("#BCBDDC","#CCC1DA","#B3A2C7","#604A7B")) +
  labs(title="Psychological Care Usage By \n Educational Pathway", x="Educational Path", y="Psychological Care Use", fill="Proportion") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  annotate("text",x=2.05, y=2.25,label=paste0("Chi-Square \n p-value = ",formatC(chiTest$p.value, format = "e", digits = 2)), size=5, family = "Garamond")+
  coord_cartesian(clip = "off")+
  theme(plot.title = element_text(hjust = 0.5),text = element_text(size=16,family="Garamond"))

``````





``````{r, warnings = FALSE}
par(mar = c(1, 1, 1, 1))
Mcontigencytable <-table(recodedTable$Classification, recodedTable$Medication_Use)
MchiTest <- chisq.test(Mcontigencytable)
MchiDf <- melt(prop.table(Mcontigencytable, margin = 1))

ggplot(data=MchiDf, aes(x=Var1, y=Var2, fill=value)) +
  geom_tile() +
  scale_fill_gradientn(colours=c("#BCBDDC","#CCC1DA","#B3A2C7","#604A7B")) +
  labs(title="Medication Use By \n Educational Pathway", x="Educational Path", y="Medication Use", fill="Proportion") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  annotate("text",x=2.05, y=2.25,label=paste0("Chi-Square \n p-value = ",round(MchiTest$p.value, digits = 3)), size=5, family = "Garamond")+
  coord_cartesian(clip = "off")+
  theme(plot.title = element_text(hjust = 0.5),text = element_text(size=16,family="Garamond"))
``````





```{r, warnings = FALSE}
recodedTable$AID <- recodedTable$ID
interest <- select(biomarkerVJoined, "C_Reactive_Protein" = H5CRP, "Creatinine_and_Cystatin_C" = H5GFRCC, "Hemoglobin_A1c" = H5HBA1C,AID)
combinedbiomarker <- left_join(data.frame(recodedTable),data.frame(unique(interest)), by= c("AID"))
combinedbiomarker <- na.omit(unique(combinedbiomarker))
```

```{r}
par(family="Garamond", cex = 1,mar = c(2, 2, 2, 2) )
hist(combinedbiomarker$Creatinine_and_Cystatin_C, main = "Creatinine and Cystatin C", xlab = "Estimated Glomerular Filtration Rate (mL/min/1.73 m2)", 
     col = "#604A7B", xlim = range(combinedbiomarker$Creatinine_and_Cystatin_C, na.rm = TRUE))
```

```{r}
par(family="Garamond", cex = 1,mar = c(2, 2, 2, 2) )
hist(combinedbiomarker$Hemoglobin_A1c, main = "Hemoglobin A1c", xlab = "Hemoglobin A1c (%)", 
     col = "#B3A2C7", xlim = range(combinedbiomarker$Hemoglobin_A1c, na.rm = TRUE))
```



```{r, warnings = FALSE}
hist(combinedbiomarker$C_Reactive_Protein, main = "C-Reactive Protein (CRP)", xlab = "CRP (mg/L)", 
     col = "#BCBDDC", xlim = range(combinedbiomarker$C_Reactive_Protein, na.rm = TRUE))

```


```{r, warnings = FALSE}
model <- lm(cbind(C_Reactive_Protein, Creatinine_and_Cystatin_C, Hemoglobin_A1c) ~ Classification, data = combinedbiomarker)

# Create scatter plot with regression line
mydf <- reshape2::melt(select(combinedbiomarker,Classification,C_Reactive_Protein, Creatinine_and_Cystatin_C, Hemoglobin_A1c), id.vars="Classification", variable.name="Variable", value.name="Value")
# Create scatterplot with regression line for each dependent variable
ggplot(mydf, aes(x = Classification, y = Value, color = Variable)) +
  geom_point() +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  scale_colour_brewer(palette = "PuBuGn")+
  stat_smooth(method = "lm", se = FALSE) +
  labs(x = "Educational Path", y = "", color = "Biomarker") +
  theme(plot.title = element_text(hjust = 0.5),text = element_text(size=9,family="Garamond"))
```
